### 2022-04-27 ms/ms.rmd
refs
Switched data around phylogeny

      # Plot a heatmap of N for each trait around the phylogeny.
      gheatmap(p1, data.matrix(matrix_data), offset = 1,  
               colnames_position="bottom", legend_title = "N", 
               colnames_angle=90, colnames_offset_y = 2, 
               hjust=0, font.size=2.5, width = 0.25, colnames = FALSE) + 
        scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
```

>>>>

      # Alternatively, summarise total effect sizes per species for acute and acclimation
      matrix_data2 <- data_long %>% filter(grepl("lnRR_Q10", name)) %>% 
                    mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full))      %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))       %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))               %>%
                      group_by(species_full, type) %>% 
                      summarise(n = n()) %>% 
                      spread(type, n, fill = 0) %>% data.frame()
                     # mutate(acclim = as.character(cut(acclim, breaks = c(0,15, 20, 25, 30, 40, 50))),
                      #        acute = as.character(cut(acute, breaks = c(0,15, 20, 25, 30, 40, 50))))

      row.names(matrix_data2) <- matrix_data2$species_full
      matrix_data2 <- matrix_data2[,2:3]

      # Plot a heatmap of N for each trait around the phylogeny.
      gheatmap(p1, data.matrix(matrix_data2), offset = 1,  
               colnames_position="bottom", legend_title = "N", 
               colnames_angle=45, colnames_offset_y = 0, 
               hjust=0, font.size=2.5, width = 0.35) + 
        scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
```

## References
